Media Matters/The Battle between Fake News and Fox News

### 2024-04-16 paper/paper.qmd
fixes

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Hannah Yu
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

library(tidyverse)
library(here)
library(rstanarm)
library(modelsummary)
library(ggplot2)
library(knitr)
library(marginaleffects)
library(plotly)
library(tibble)
library(margins)
library(testthat)
library(kableExtra)
library(arrow)
library(gridExtra)

@@

```{r}
ces2020 <-  read_parquet(here::here("data/analysis_data/cleaned_ces2020.parquet"))
```

@@

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

https://onlinelibrary.wiley.com/doi/full/10.1111/j.1467-9477.2011.00284.x

@@

Data analysis is performed using statistical programming language R [@citeR], with packages `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat] and `kableExtra` [@citeKableExtra].

@@

Data for this research comes from the 2020 Cooperative Election Study (CES) [@citeCes2020], a annual US political survey. The CES contains information about Americans' political view, voting behaviours and experiences across various political geography and social context. 61,000 American adults participated in the survey in 2020.

@@

Since this paper focuses on analyzing the influence of media usage on registered voters decision, I perform the following data cleaning process and selected the related variables. The dataset is cleaned by renaming the column names, changing the variable for from categorical to dummy, selecting the variables of interest, and filtering out missing information and information not related to the study. After cleaning, there are 10331 rows of data remain in the cleaned dataset.  @tbl-clean-data shows a preview of the cleaned dataset.

The dependent variable of my examination is: `presvote20post`, renamed to `voted_for`. This variable represents the presidential candidate the respondent voted for in the 2020 election in the form of a numerical variable. The variable `votereg` represents whether the respondent is registered to vote using numerical numbers. This paper will only analyze respondents who are registered to vote and focus on the outcome of two candidates, Joe Biden representing the Democratic party and Donald Trump representing the Republican party. To analyze the observations of interest, I first limited the observations to the ones that responded "Yes" in `votereg`. And I filtered the responses in `presvote20post` to only "Biden" or "Trump" and converted the variable into a dummy variable where 1 represents "Biden" and 0 represents "Trump". Rest of the variable this paper focuses on are being divided into three categories: Media Use - Networks, Media Use - TV Type, and Party Affiliation.

@@

    -   This variable reports on what kind of TV news the respondent watches. A value of 1 signifies that the respondent watches "Local Newcast", 2 signifies "National Newscast"; 3 "Both".

@@

    -   This variable reports if the respondent political party affiliation. A value of 1 signifies that the respondent identifies as "Democrat", 2 signifies "Republican"; 3 "Independent", and 4 "Other".

```{r}
#| label: tbl-summary
#| tbl-cap: "Statistics summary of the cleaned 2020 CES dataset"
#| message: false
#| echo: false

ces2020 |>
  summary() |>
  kable() |>
  kable_styling()

```
@tbl-summary presents a summary of the cleaned data, showing detailed statistics about the dataset. It is evident that Biden has more supporters in this election. The seven listed media networks capture the majority networks people watch; while `Other` captures the rest. Due to the small number of respondents that only watch local newscast and missing values associated with this variable, the number of respondents that only watches local newscast becomes 0 after cleaning. Therefore, the value "Local Newscast" is excluded from later examinations and modelings. There are more respondents identifying as Democrat than than any other party. There are almost equal amount of Republicans and Independent voters; and only 534 voters identified as "Other."

## Data Measurement

Because the data was collected from surveys, there might be some inconsistencies and misinterpretations of the questions in people's responses. Therefore this section disects on what the variables are measuring.

each of our variable is only representable for the following scenarios.

Firstly, for the variable `votereg` indicating whether a respondent is registered to vote, the variable relies on self-reported information from survey respondents. Due to the inefficiencies of the US voter registration system, people who misunderstood their voter registration status might falsely reported their condition. For example, some individuals might believe they reached the status simply because they are of age but did not actually register at their local office. According to @inaccurate, there are millions of voter registrations that are no longer valid or inaccurate.

Representing the presidential candidate the respondent voted for, `CC20_410` takes into account of recall bias and social desirability bias along with people's reported presidential candidate preference. Trump had made many controversial speeches throughout his presidency that contributed to his polarizing image and unpopularity in mainstream media. Therefore, many of his voters would conceal their support due to social pressure, potentially leading to under-reporting of votes for Trump in the survey data.

People's media use networks is being represented by if  `ABC`, `CBS`, `NBC`, `CNN`, `Fox_News`, `MSNBC`, `PBS`, and `Other`. Relying on people's self-reported preferences, these variables are also subject to recall bias. Respondents might overestimate or underestimate their consumptions of certain network based on the content. They might only report the network which reported news that left a strong impression on them. In addition, respondents might choose to conceal their consumptions of certain media networks due to the network's political affiliation or reputation.

`TV_type` reports the respondents' preference in local newscast or national newscast (or both). The main concern over this variable lies in the fact that after data cleaning, the number of respondents exclusively watching local newscasts became zero due to missing values associated with this variable. The fact that many missing values are related to this variable could have unobservable implications that require future examinations. Therefore this study excludes the effect of only watching local newscast, and centers on people either only consume national newscast or both.

The variable `Party` categories respondents into four categories. Only having four categories might overlook the nuanced and diverse political beliefs held by individuals. Some may have hybrid or unconventional political views that don't fit neatly into these categories. Therefore, their categorization might not accurately describe their party affiliations.

# Model

@@

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

I utilized a Bayesian logistic regression model to examine the relationship between voters' political preferences and their media use preferences.The model is formulated as follows:

\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{ABC}_i + \beta_2 \times \mbox{CBS}_i + \beta_3 \times \mbox{NBC}_i + \beta_4 \times \mbox{CNN}_i + \beta_5 \times \mbox{Fox_News}_i + \beta_6 \times \mbox{MSNBC}_i + \beta_7 \times \mbox{PBS}_i + \beta_8 \times \mbox{Other}_i + \beta_9 \times \mbox{TV_type}_i + \beta_{10} \times \mbox{Party}_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
\beta_3 &\sim \mbox{Normal}(0, 2.5) \\
\beta_4 &\sim \mbox{Normal}(0, 2.5) \\
\beta_5 &\sim \mbox{Normal}(0, 2.5) \\
\beta_6 &\sim \mbox{Normal}(0, 2.5) \\
\beta_7 &\sim \mbox{Normal}(0, 2.5) \\
\beta_8 &\sim \mbox{Normal}(0, 2.5) \\
\beta_9 &\sim \mbox{Normal}(0, 2.5) \\
\beta_10 &\sim \mbox{Normal}(0, 2.5)
\end{align}

In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted Biden (as opposed to Trump). The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_10$)) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively. Media use networks are being represented by the following predictor variables: \text{ABC}_i, \text{CBS}_i, \text{NBC}_i, \text{CNN}_i, \text{Fox_News}_i \text{MSNBC}_i ,\text{PBS}_i, and \text{Other}_i. The rest of the predictor variables are denoted as \text{TV_type}_i and \text{Party}_i, where $i$ indexes the individuals in the dataset.

@@

### Model justification

A positive relationship between watching left leaning (Democrat) media networks and voting for Biden; and a similar positive relationship between watching right leaning (Republican) media networks and voting for Trump. In particular, according to @grieco2020americans, among the 7 networks identified in this study, Fox News is known as the most conservative media network while CNN and MSNBC stand as leading liberal media. Slightly leaning left, ABC, CBS, and NBC are generally neutral. PBS is also more liberal and Democratic leaning, but not as extreme as CNN or MSNBC [@blake2014ranking]. This is assumption is made based on the findings that state exposure to media network would have a influence on voter [@wettstein2017media].

As most news and media outlets are more liberal leaning, I expect a slightly higher chance of voting for Biden for voters who watch both local and national newscasts. Local newscast might be more be perceived as more trustworthy and more community oriented; therefore, viewers may tend accept content and political opinions from local newscast more easily. On the other hand, voters who exclusively watch national news may adopt a more cautious approach and be less inclined to uncritically accept the material presented to them. Therefore, voters who watch both local and national newscasts might have a slightly higher chance of supporting Biden.

In terms of the relationship of party affiliation and voting choices. There is an easy assumption; the majority of Democrat voters would vote for their candidate Biden, and almost all Republicans voting for Trump. I except a even voting outcomes from Independent and Other voters as they have not express their preferences between the two.

In terms of the relationship between party affiliation and voting choices, it's reasonable to expect that the majority of Democrat voters would support their candidate, Biden, while a significant portion of Republican voters would favor Trump. This expectation is based on historical voting patterns and the ideological alignment between these parties and their respective candidates. However, it's less predictable how Independent and Other voters might vote, as they have not explicitly expressed their preferences between the two main candidates. Therefore, I anticipate half of the votes go to Biden and half to Trump.

```{r}

ggplot(ces2020, aes(x = factor(voted_for), fill = PBS)) +
  geom_bar(position = "dodge") +
  labs(title = "PBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal()
```

# Results

## Data Results

```{r, fig.height = 10, fig.width = 10}
#| label: fig-network
#| fig-cap: Distribution of Presidential Preferences by Network
#| echo: false
#| warning: false
#| message: false
#| 
# Create individual plots for each news channel
plot_ABC <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(ABC))) +
  geom_bar(position = "dodge") +
  labs(title = "ABC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal() 
  #guides(fill = FALSE)

plot_CBS <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(CBS))) +
  geom_bar(position = "dodge") +
  labs(title = "CBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal() #+
 # facet_wrap(~ ., ncol = 4) +
  #guides(fill = FALSE)

plot_NBC <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(NBC))) +
  geom_bar(position = "dodge") +
  labs(title = "NBC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal() #+
 # facet_wrap(~ ., ncol = 4) +
  #guides(fill = FALSE)

plot_CNN <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(CNN))) +
  geom_bar(position = "dodge") +
  labs(title = "CNN", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal() #+
 # facet_wrap(~ ., ncol = 4) +
  #guides(fill = FALSE)

plot_Fox_News <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(Fox_News))) +
  geom_bar(position = "dodge") +
  labs(title = "Fox News", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal()# +
#  facet_wrap(~ ., ncol = 4) +
 # guides(fill = FALSE)

plot_MSNBC <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(MSNBC))) +
  geom_bar(position = "dodge") +
  labs(title = "MSNBC", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal()# +
#  facet_wrap(~ ., ncol = 4) +
  #guides(fill = FALSE)

plot_PBS <- ggplot(ces2020, aes(x = factor(voted_for), fill = PBS)) +
  geom_bar(position = "dodge") +
  labs(title = "PBS", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal()

plot_Other <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(Other))) +
  geom_bar(position = "dodge") +
  labs(title = "Other", x = "Voted for Biden (1) or Trump (0)", y = "Count") +
  theme_minimal()# +
  #guides(fill = FALSE)

#grid.arrange(plot_ABC, plot_CBS, plot_NBC, plot_CNN, plot_Fox_News, plot_MSNBC, plot_PBS + #theme(legend.position ='none'), plot_Other, legend, nrow = 3)

```
```{r, fig.height = 10, fig.width = 10}
#| label: fig-network
#| fig-cap: Distribution of Presidential Preferences by Network
#| echo: false
#| warning: false
#| message: false
# Create individual plots for each news channel
plot_ABC <- ggplot(ces2020, aes(x = factor(ABC), fill = factor(voted_for))) +
  geom_bar(position = "dodge") +
  labs(title = "ABC", x = "ABC", y = "Count") +
  scale_fill_manual(values = c("red", "blue")) +  # Specify colors for Biden and Trump
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally

@@

@fig-network depicts the relationship between voters voting preference and media network preference. Because more voters voted for Biden, Biden supporters seem to watch more media network overall. Therefore, I examine the proportions of voters watching a specific network and voting for one of the two candidates. Biden supporters have a higher proportions of watching most networks. Among all the networks that have higher proportions of Biden voters, CNN and MSNBC, two of the most Democratic leaning news networks, have a significantly higher proportions of viewers that are Biden supporters and barely any viewers that support Trump. The only network that is being consumed by Trump supporters are Fox News, a network know to be Republican leaning.

```{r, fig.height = 6.6, fig.width = 10}

# Create individual plots for each news channel
# plot_post <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(post))) +
#   geom_bar(position = "dodge") +
#   labs(title = "Posted", x = "Vote", y = "Count") +
#   theme_minimal() +
#   theme(plot.title = element_text(hjust = 0.5)) +
#   coord_cartesian(ylim = c(0, 4000)) +  
#   guides(fill = FALSE)
# 
# plot_comment <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(comment))) +
#   geom_bar(position = "dodge") +
#   labs(title = "Commented", x = "Vote", y = "Count") +
#   theme_minimal() +
#   coord_cartesian(ylim = c(0, 4000)) +  
#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
#  # facet_wrap(~ ., ncol = 4) +
#   guides(fill = FALSE)
# 
# plot_read <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(read))) +
#   geom_bar(position = "dodge") +
#   labs(title = "Read", x = "Vote", y = "Count") +
#   theme_minimal() +
#   coord_cartesian(ylim = c(0, 4000)) +
#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
#  # facet_wrap(~ ., ncol = 4) +
#   guides(fill = FALSE)
# 
# plot_follow <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(follow))) +
#   geom_bar(position = "dodge") +
#   labs(title = "Followed", x = "Vote", y = "Count") +
#   theme_minimal() +
#   coord_cartesian(ylim = c(0, 4000)) +
#   theme(plot.title = element_text(hjust = 0.5)) +
#  # facet_wrap(~ ., ncol = 4) +
#   guides(fill = FALSE)
# 
# plot_forward <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(forward))) +
#   geom_bar(position = "dodge") +
#   labs(title = "Forwarded", x = "Vote", y = "Count") +
#   coord_cartesian(ylim = c(0, 4000)) +
#   theme_minimal() +
#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) 
# 
# 
# legend <- g_legend(plot_forward + theme(legend.position='bottom', 
#                                         legend.text = element_text(size = 15, face="bold"), 
#                                         legend.title = element_blank()))
# 
# grid.arrange(plot_post, plot_comment, plot_read, plot_follow, plot_forward + theme(legend.position ='none'), legend, nrow = 2)

```{r}
# Create individual plots for each news channel
# plot_post <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(post, levels = c("not_selected", "selected")))) +
#   geom_bar(position = "stack", stat = "count") +
#   labs(title = "Posted", x = "Vote", y = "Count") +
#   theme_minimal() +
#   theme(plot.title = element_text(hjust = 0.5)) +
#   coord_cartesian(ylim = c(0, 6000)) +  
#   guides(fill = FALSE)
# 
# plot_comment <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(comment, levels = c("not_selected", "selected")))) +
#   geom_bar(position = "stack", stat = "count") +
#   labs(title = "Commented", x = "Vote", y = "Count") +
#   theme_minimal() +
#   coord_cartesian(ylim = c(0, 6000)) +  
#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
#   guides(fill = FALSE)
# 
# plot_read <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(read, levels = c("not_selected", "selected")))) +
#   geom_bar(position = "stack", stat = "count") +
#   labs(title = "Read", x = "Vote", y = "Count") +
#   theme_minimal() +
#   coord_cartesian(ylim = c(0, 6000)) +
#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
#   guides(fill = FALSE)
# 
# plot_follow <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(follow, levels = c("not_selected", "selected")))) +
#   geom_bar(position = "stack", stat = "count") +
#   labs(title = "Followed", x = "Vote", y = "Count") +
#   theme_minimal() +
#   coord_cartesian(ylim = c(0, 6000)) +
#   theme(plot.title = element_text(hjust = 0.5)) +
#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) +
#   guides(fill = FALSE)
# 
# plot_forward <- ggplot(ces2020, aes(x = factor(voted_for), fill = factor(forward, levels = c("not_selected", "selected")))) +
#   geom_bar(position = "stack", stat = "count") +
#   labs(title = "Forwarded", x = "Vote", y = "Count") +
#   coord_cartesian(ylim = c(0, 6000)) +
#   theme_minimal() +
#   theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.title = element_text(hjust = 0.5)) 
#  # facet_wrap(~ ., ncol = 4) +
# 
# 
# #legend <- g_legend(plot_forward + theme(legend.position='bottom', 
#                                         #legend.text = element_text(size = 15, face="bold"), 
#                                        # legend.title = element_blank())
# 
# grid.arrange(plot_post, plot_comment, plot_read, plot_follow, plot_forward + theme(legend.position ='none'), nrow = 1)

>>>>

---
title: "Media Matters/The Battle between Fake News and Fox News"
subtitle: "Exploring the Influence of Media Preferences on Voting Behavior in the 2020 U.S. Presidential Election Among Voters from Different Parties"
author: 
  - Hannah Yu
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(here)
library(rstanarm)
library(modelsummary)
library(ggplot2)
library(knitr)
library(marginaleffects)
library(plotly)
library(tibble)
library(margins)
library(testthat)
library(kableExtra)
library(arrow)
library(gridExtra)
library(pander)

@@

```{r}
#| include: false
#| warning: false
#| message: false
ces2020 <-  read_parquet(here::here("data/analysis_data/cleaned_ces2020.parquet"))
```

@@

The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; 6) why it is important; 7) the structure of the paper. A reader should be able to read only the introduction and know what was done, why, and what was found. Likely 3 or 4 paragraphs, or 10 per cent of total.

# Introduction
The 2020 U.S. presidential election, between Republican candidate and incumbent President Donald Trump, and Democratic candidate and former Vice President Joe Biden, was one of the most intense in recent history. Trump's divisive and highly controversial statements while in office, as well as his administration's mishandling of the pandemic, widened the divide between the two parties during this election period. This division was also reflected in the media outlets favored by each party, with Fox News being known as the conservative media network highly favored by Republicans, while CNN leads as the Democrats' favorite. Often, media outlets on both sides presented differing narratives on the same events, with each side unwilling to concede.

The division of media was exacerbated by Trump's animosity against liberal networks. Trump famously labeled any unflattering issues that might work against him as "Fake News," regardless of their actual validity [@timm2020trump]. He even handed out the "Fake News Award" through Twitter to several notable liberal media outlets, including CNN [@siddiqui2018trump]. On the other hand, Democrats also have long-standing feuds with the Republican network Fox News. Biden has referred to Fox News as "one of the most destructive forces in the United States" [@stelter2022biden]. With clear political alliances and agendas, these different media outlets might subtly influence their viewers' political ideology and voting decisions. Therefore, it is important to explore whether these media networks do indeed have influences on election outcomes and, if so, the magnitude of that effect. A good understanding of this relationship could enable voters to be more critical of the media they consume.

To explore and answer these questions, this paper analyzes the influence of watching specific media on voters' voting behavior. It uses the 2020 US election data from the Cooperative Election Study (CES), which surveys Americans before and after elections. From the dataset, information on voters' media preferences on America's most prominent networks, including ABC, CNN, Fox News, etc., was gathered. Then, a Bayesian logistic regression model was employed to estimate the election outcome between Trump and Biden based on voters' media preferences and their original party affiliation. The estimand of this paper is the actual number of people who supported Trump or Biden during the 2020 election. However, due to the difficulty of collecting data on millions of voters, this paper estimates the estimand using the logistic regression model trained using a sample from the CES dataset. The findings indicate that watching media networks with specific political ideologies is associated with higher chances of voting for the candidate they prefer. Among all networks, this relationship is most apparent in CNN and Fox News, exerting heavy influence on voters who classify as "Independent" or "Other." Additionally, this paper also studies the influence of watching national newscasts on voting outcomes compared to watching both national and local newscasts, finding no significant differences between the outcomes of the two.

The remainder of this paper is structured as follows: @sec-data demonstrates the data used for this paper, @sec-model builds the model and discusses its justification and explanation, @sec-result highlights the results of the predictions using tables and graphs, and @sec-discussion contains discussions conducted based on the findings. These discussions address the voting prediction results based on TV types, party affiliation, and media influence, and discuss policy implications from the study.

@@

Data analysis is performed using statistical programming language R [@citeR], with packages `tidyverse` [@citeTidyverse], `here` [@citeHere], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `marginaleffects` [@citeMarginalEffects], `plotly` [@citePlotly], `tibble` [@citeTibble], `margins` [@citeMargins], `testthat` [@citetestthat], `kableExtra` [@citeKableExtra], `arrow` [@citeArrow], `gridExtra` [@citeGridExtra], and `pander` [@citePander].

@@

Data for this research comes from the 2020 Cooperative Election Study (CES) [@citeCes2020], an annual US political survey. The CES contains information about Americans' political views, voting behaviours and experiences across various political geography and social contexts. 61,000 American adults participated in the survey in 2020.

@@

Since this paper focuses on analyzing the influence of media usage on registered voters' decisions, I performed the following data-cleaning process and selected the related variables. The dataset is cleaned by renaming the column names, changing the variable from categorical to dummy, selecting the variables of interest, and filtering out missing information and information not related to the study. After cleaning, there are 10331 rows of data remaining in the cleaned dataset. @tbl-clean-data shows a preview of the cleaned dataset.

The dependent variable of my examination is: `presvote20post`, renamed to `voted_for`. This variable represents the presidential candidate the respondent voted for in the 2020 election in the form of a numerical variable. The variable `votereg` represents whether the respondent is registered to vote using numerical numbers. This paper will only analyze respondents who are registered to vote and focus on the outcome of two candidates, Joe Biden representing the Democratic party and Donald Trump representing the Republican party. To analyze the observations of interest, I first limited the observations to the ones that responded "Yes" in `votereg`. And I filtered the responses in `presvote20post` to only "Biden" or "Trump" and converted the variable into a dummy variable where 1 represents "Biden" and 0 represents "Trump". The rest of the variables this paper focuses on are being divided into three categories: Media Use - Networks, Media Use - TV Type, and Party Affiliation.

@@

    -   This variable reports on what kind of TV news the respondent watches. A value of 1 signifies that the respondent only watches "Local Newcast", 2 signifies "National Newscast"; 3 "Both".

@@

    -   This variable reports the respondent political party affiliation. A value of 1 signifies that the respondent identifies as "Democrat", 2 signifies "Republican"; 3 is "Independent", and 4 is "Other".

```{r}
#| label: tbl-summary
#| tbl-cap: "Statistics summary of the cleaned 2020 CES dataset"
#| message: false
#| echo: false
#| warning: false

summary <- 
  ces2020 |>
  summary() |>
  kable()

# Convert the summary to a data frame
summary_df <- as.data.frame(summary)

# Print the summary using pander
pander(summary_df, style = "grid", split.tables = Inf)

```
@tbl-summary presents a summary of the cleaned data, showing detailed statistics about the dataset. It is evident that Biden has more supporters in this election. The seven listed media networks capture the majority of networks people watch; while `Other` captures the rest. Due to the conflict of "Local Newscast" with the variables for media use networks, the number of respondents that only watch local newscast becomes 0 after cleaning. If the respondent only watches local newscasts, then they would skip all the questions related to national newscasts (e.g. Do you watch ABC?) since these questions are not applicable. With no further media-related information for voters who only watch local newscasts, this value is excluded from later examinations and modelling. There are more respondents identifying as Democrats than any other party. There are almost equal amount of Republicans and Independent voters, and only 534 voters identified as "Other."

## Data Measurement
Because the data was collected from surveys, there might be some inconsistencies and misinterpretations of the questions in people's responses. Therefore this section discusses what the variables are measuring.

Firstly, for the variable `votereg` indicating whether a respondent is registered to vote, the variable relies on self-reported information from survey respondents. Due to the inefficiencies of the US voter registration system, people who misunderstood their voter registration status might falsely report their condition. For example, some individuals might believe they reached the status simply because they are of age but did not actually register at their local office. According to @inaccurate, there are millions of voter registrations that are no longer valid or inaccurate.

Representing the presidential candidate the respondent voted for, `CC20_410` considers recall bias, social desirability bias, and people's reported presidential candidate preference. Trump had made many controversial speeches throughout his presidency that contributed to his polarizing image and unpopularity in mainstream media. Therefore, many of his voters would conceal their support due to social pressure, potentially leading to under-reporting of votes for Trump in the survey data.

People's media use networks are represented by if  `ABC`, `CBS`, `NBC`, `CNN`, `Fox_News`, `MSNBC`, `PBS`, and `Other`. Relying on people's self-reported preferences, these variables are also subject to recall bias. Respondents might overestimate or underestimate their consumption of certain networks based on the content. They might only report the network which reported news that left a strong impression on them. In addition, respondents might choose to conceal their consumption of certain media networks due to the network's political affiliation or reputation.

`TV_type` reports the respondents' preference for local newscasts or national newscasts (or both). The main concern over this variable lies in the fact that voters who only watch local newscasts are filtered out of the dataset. Because filtering this value out is necessary for the examinations of the influence of other media networks, this study excludes the effect of only watching local newscasts and centers on people who either only consume national newscasts or both.

The variable `Party` categorizes respondents into four categories. "Democrat" means the voter identifies as a Democrat; "Republican" if the voter identifies themselves as a Republican. However, in this dataset, "Independent" is not affiliated with the American Independent Party; independent here means the voter has no party affiliation. Lastly, "Other" symbolizes the voter being part of a party that is neither Democratic nor Republican. Only having four categories might overlook the nuanced and diverse political beliefs held by individuals. Some may have hybrid or unconventional political views that don't fit neatly into these categories. Therefore, their categorization might not accurately describe their party affiliations.

# Model {@sec-model}

@@

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix - @sec-model-details].

@@

I utilized a Bayesian logistic regression model to examine the relationship between voters' political preferences and their media use preferences. The model is formulated as follows:

\begin{align}
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{ABC}_i + \beta_2 \times \mbox{CBS}_i + \beta_3 \times \mbox{NBC}_i \nonumber \\
&\quad + \beta_4 \times \mbox{CNN}_i + \beta_5 \times \mbox{Fox\_News}_i + \beta_6 \times \mbox{MSNBC}_i \nonumber \\
&\quad + \beta_7 \times \mbox{PBS}_i + \beta_8 \times \mbox{Other}_i + \beta_9 \times \mbox{TV\_type}_i + \beta_{10} \times \mbox{Party}_i \nonumber \\
\alpha &\sim \mbox{Normal}(0, 2.5) \nonumber \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
\beta_3 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
\beta_4 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
\beta_5 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
\beta_6 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
\beta_7 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
\beta_8 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
\beta_9 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
\beta_{10} &\sim \mbox{Normal}(0, 2.5) \nonumber
\end{align}

In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted Biden (as opposed to Trump). The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_10$)) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively. Media use networks are being represented by the following predictor variables:  \text{ABC}_i, \text{CBS}_i, \text{NBC}_i, \text{CNN}_i, \text{Fox\_News}_i, \text{MSNBC}_i, $\text{PBS}_i$, \text{Other}_i. The rest of the predictor variables are denoted as \text{TV\_type}_i and \text{Party}_i, where $i$ indexes the individuals in the dataset.

@@

### Model justification
A positive relationship is expected between watching left-leaning (Democrat) media networks and voting for Biden, as well as a similar positive relationship between watching right-leaning (Republican) media networks and voting for Trump. According to @grieco2020americans, among the 7 networks identified in this study, Fox News is known as the most conservative media network, while CNN and MSNBC are leading liberal media outlets. Slightly leaning left, ABC, CBS, and NBC are generally considered neutral. PBS is also more liberal and Democratic-leaning, but not as extreme as CNN or MSNBC [@blake2014ranking]. This assumption is grounded in findings that suggest exposure to media networks influences voters [@wettstein2017media].

As most news and media outlets are more liberal-leaning, I expect a slightly higher chance of voting for Biden for voters who watch both local and national newscasts. Local newscasts might be more be perceived as more trustworthy and more community-oriented; therefore, viewers may tend to accept content and political opinions from local newscasts more easily. On the other hand, voters who exclusively watch national news may adopt a more cautious approach and be less inclined to uncritically accept the material presented to them. Therefore, voters who watch both local and national newscasts might have a slightly higher chance of supporting Biden. 
In terms of the relationship between party affiliation and voting choices, it's reasonable to expect that the majority of Democrat voters would support their candidate, Biden, while a significant portion of Republican voters would favour Trump. This expectation is based on historical voting patterns and the ideological alignment between these parties and their respective candidates. However, it's less predictable how Independent and Other voters might vote, as they have not explicitly expressed their preferences between the two main candidates. Therefore, I anticipate an equal split of votes between Biden and Trump for these two groups.

# Results {@sec-results}

## Data Results
```{r}
#| echo: false
#| warning: false
#| message: false
# Function to extract legend from a ggplot object
g_legend <- function(a.gplot) {
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

```{r, fig.height = 10, fig.width = 10}
#| label: fig-network
#| fig-cap: Distribution of Presidential Preferences by Network
#| echo: false
#| warning: false
#| message: false

#Create individual plots for each news channel
plot_ABC <- ggplot(ces2020, aes(x = factor(ABC), fill = factor(voted_for))) +
  geom_bar(position = "dodge") +
  labs(title = "ABC", x = "ABC", y = "Count") +
  scale_fill_manual(values = c("red", "blue")) +  # Specify colors for Biden and Trump
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.5))  # Center the title horizontally

@@

@fig-network depicts the relationship between voters' voting preference and media network preference. Given that more voters supported Biden, it's evident that Biden supporters tend to watch more media networks overall. Consequently, I analyze the proportions of voters watching specific networks and their voting preferences.  Biden supporters have higher proportions of watching most networks. Among all the networks that have higher proportions of Biden voters, CNN and MSNBC, two of the most Democratic-leaning news networks, have significantly higher proportions of viewers that are Biden supporters and barely any viewers that support Trump. The only network that is being consumed by Trump supporters is Fox News, a network known to be Republican-leaning.
